Emitter Source Geolocation from Imparted Rotor Blade Modulation

### 2016-10-15 MSc. Thesis Template.tex
add symbols list

%% ----------------------------------------------------------------
\setstretch{1.5}  % Set the line spacing to 1.5, this makes the following tables easier to read
%\clearpage  % Start a new page
\lhead{\emph{Abbreviations}}  % Set the left side page header to "Abbreviations"
\listofsymbols{ll}  % Include a list of Abbreviations (a table of two columns)
{
 %\textbf{Acronym} & \textbf{W}hat (it) \textbf{S}tands \textbf{F}or \\
 \textbf{2D} & 2-\textbf{D}imensional \\
 \textbf{3D} & 3-\textbf{D}imensional \\
 \textbf{BER} & \textbf{B}it \textbf{E}error \textbf{R}ate \\
 \textbf{BRDF} & \textbf{B}i-directional \textbf{R}eflection  \textbf{D}istrobution \textbf{F}unction \\
 \textbf{CSV} & \textbf{C}omma \textbf{S}eparated \textbf{V}alue \\
 \textbf{DSP} & \textbf{D}igital \textbf{S}ignal \textbf{P}rocessing \\
 \textbf{GPS} & \textbf{G}lobal \textbf{P}ositioning \textbf{S}ystem \\
 \textbf{GPU} & \textbf{G}raphics \textbf{P}rocessing \textbf{U}nit \\
 \textbf{GUI} & \textbf{G}raphical \textbf{U}ser \textbf{I}nterface \\
 \textbf{IQ} & \textbf{I}n-phase and \textbf{Q}uadrature \\
 \textbf{JEM} & \textbf{J}et \textbf{E}ngine \textbf{M}odulation \\
 \textbf{LOS} & \textbf{L}ine \textbf{O}f \textbf{S}ight \\
 \textbf{RBM} & \textbf{R}otor \textbf{B}lade \textbf{M}odulation \\
 \textbf{RF} & \textbf{R}adio \textbf{F}requency \\
 \textbf{RPM} & \textbf{R}otations \textbf{P}er \textbf{M}inute \\
 \textbf{Rx} & \textbf{R}eceiver \\
 \textbf{STFT} & \textbf{S}hort \textbf{T}ime \textbf{F}ourier \textbf{T}ransform \\ 
 \textbf{Tx} & \textbf{T}ransmitter \\

@@

%% ----------------------------------------------------------------
%\clearpage  % Start a new page
%\lhead{\emph{Mathematical Notations}}  % Set the left side page header to "Physical Constants"
%\listofconstants{ll}  % Include a list of Physical Constants (a four column table)
{
% Constant Name & Symbol & = & Constant Value (with units) \\

%% ----------------------------------------------------------------
%\clearpage  %Start a new page
%\lhead{\emph{Symbols}}  % Set the left side page header to "Symbols"
%\listofnomenclature{ll}  % Include a list of Symbols (a three column table)
{
% symbol & name & unit \\

}
%% ----------------------------------------------------------------
% End of the pre-able, contents and lists of things
% The Abstract Page
\addtotoc{Abstract}  % Add the "Abstract" page entry to the Contents
\abstract{
\addtocontents{toc}{\vspace{1em}}  % Add a gap in the Contents, for aesthetics
In RF communications with a rotorcraft, such as a helicopter, the rotor blades can impart a modulation onto the received signal called Rotor Blade Modulation (RBM). This modulation is caused by the reflection of a signal off the rotating blades. The reflected signal is Doppler shifted based on where the signal is reflected along the length of the blade as well as the angle between the axis of rotation and the emitter. RBM is known to degrade the performance of RF communications on rotorcraft and can be used in radar applications to detect and classify aircraft, but there is little on its usefulness in other areas. This thesis looks at the ability to utilize the RBM phenomenon on the rotorcraft itself to geo-locate and track a signal emitter on the ground.

>>>>

%% ----------------------------------------------------------------
\setstretch{1.5}  % Set the line spacing to 1.5, this makes the following tables easier to read
\clearpage  % Start a new page
\lhead{\emph{Abbreviations}}  % Set the left side page header to "Abbreviations"
\listofsymbols{ll}  % Include a list of Abbreviations (a table of two columns)
{
 %\textbf{Acronym} & \textbf{W}hat (it) \textbf{S}tands \textbf{F}or \\
 \textbf{2D} & 2-\textbf{D}imensional \\
 \textbf{3D} & 3-\textbf{D}imensional \\
 \textbf{BER} & \textbf{B}it \textbf{E}error \textbf{R}ate \\
 \textbf{BRDF} & \textbf{B}i-directional \textbf{R}eflection  \textbf{D}istrobution \textbf{F}unction \\
 \textbf{CSV} & \textbf{C}omma \textbf{S}eparated \textbf{V}alue \\
 \textbf{DSP} & \textbf{D}igital \textbf{S}ignal \textbf{P}rocessing \\
 \textbf{GPS} & \textbf{G}lobal \textbf{P}ositioning \textbf{S}ystem \\
 \textbf{GPU} & \textbf{G}raphics \textbf{P}rocessing \textbf{U}nit \\
 \textbf{GUI} & \textbf{G}raphical \textbf{U}ser \textbf{I}nterface \\
 \textbf{IQ} & \textbf{I}n-phase and \textbf{Q}uadrature \\
 \textbf{JEM} & \textbf{J}et \textbf{E}ngine \textbf{M}odulation \\
 \textbf{LOS} & \textbf{L}ine \textbf{O}f \textbf{S}ight \\
 \textbf{RBM} & \textbf{R}otor \textbf{B}lade \textbf{M}odulation \\
 \textbf{RF} & \textbf{R}adio \textbf{F}requency \\
 \textbf{RPM} & \textbf{R}otations \textbf{P}er \textbf{M}inute \\
 \textbf{Rx} & \textbf{R}eceiver \\
 \textbf{STFT} & \textbf{S}hort \textbf{T}ime \textbf{F}ourier \textbf{T}ransform \\ 
 \textbf{Tx} & \textbf{T}ransmitter \\

@@

%% ----------------------------------------------------------------
%\clearpage  % Start a new page
%\lhead{\emph{Mathematical Notations}}  % Set the left side page header to "Physical Constants"
%\listofconstants{ll}  % Include a list of Physical Constants (a four column table)
%{
% Constant Name & Symbol & = & Constant Value (with units) \\

%}

%% ----------------------------------------------------------------
\clearpage  %Start a new page
\lhead{\emph{Symbols}}  % Set the left side page header to "Symbols"
\listofnomenclature{l p{5cm} l}  % Include a list of Symbols (a three column table)
{
 \textbf{Symbol} & \textbf{Name} & \textbf{Units} \\
 $\theta_{El}$ & Transmitter Elevation angle & degrees \\
 $\theta_{r}$ & Ray Reflection angle & degrees \\
 $\theta_{Az}$ & Transmitter Azimuth angle & degrees \\
 $f_d$ & Doppler Frequency shift & Hz \\
 $\theta_b$ & Rotor Blade angle & degrees \\
 $Rx_x$ & Receiver position in X axis & meters \\
 $Rx_y$ & Receiver position in Y axis & meters \\
 $Rx_z$ & Receiver position in Z axis & meters \\
 $G_r$ & & \\
 $G_t$ & & \\
 $R$ & & \\
 $n$ & & \\
 $d_i$ & & \\
 $\theta_i$ & Angle of incedence with an objects normal & radians \\
 $d$ & Total distance traveled by a ray & meters \\ 
 $t_0$ & Starting time in a frame & seconds \\
 $r$ & A radius along the length of the blade & meters \\
 $\omega_r$ & Rotational velocity of the blade & rad/second \\
 $F$ & Fading coefficient & \\
 $\lambda$ & Wavelength & meters \\
 $c$ & Speed of Light & meters/seconds \\
 $f$ & frequency & Hz \\
 $f_0$ & initial frequency & Hz \\
 $f_s$ & sampling frequency & samples/seconds \\
 $EnvelopeDifference$ & difference between two doppler envelopes & Hz \\
 $MaxUpperEnvelope$ & Array of values corresponding to the maximum of each azimuth or elevation upper envelope calculation & Hz \\
 $MinLowerEnvelope$ & Array of values corresponding to the minimum of each azimuth or elevation lower envelope calculation & Hz \\
 $BladeLength$ & Length of single rotor blade (radius of rotor) & meters \\
 $f_c$ & Center Frequency & Hz \\
 $R_{Estimate}$ & Estimated reflection radius & meters \\
 $f_{DopplerMax}$ & The maximum amount of doppler for a particular blade length and RPM & Hz \\
 $f_{DopplerCorrect}$ & The corrected doppler per $\theta_{Az}$ to be processed & Hz \\
 $A_{shift}$ & The amount of shift needed to correct for Blade pitch & Hz \\
}
%% ----------------------------------------------------------------
% End of the pre-able, contents and lists of things
% The Abstract Page
\addtotoc{Abstract}  % Add the "Abstract" page entry to the Contents
\abstract{
\addtocontents{toc}{\vspace{1em}}  % Add a gap in the Contents, for aesthetics
In RF communications with a rotorcraft, such as a helicopter, the rotor blades can impart a modulation onto the received signal called Rotor Blade Modulation (RBM). This modulation is caused by the reflection of a signal off the rotating blades. The reflected signal is Doppler shifted based on where the signal is reflected along the length of the blade as well as the angle between the axis of rotation and the emitter. RBM is known to degrade the performance of RF communications on rotorcraft and can be used in radar applications to detect and classify aircraft, but there is little on its usefulness in other areas. This thesis looks at the ability to utilize the RBM phenomenon on the rotorcraft itself to geo-locate and track a signal emitter on the ground.
